---
title: "DATA 605 HW 7"
author: "Yohannes Deboch"
date: "March 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Let X1, X2, . . . , Xn be n mutually independent random variables, each of
which is uniformly distributed on the integers from 1 to k. Let Y denote the
minimum of the Xi’s. Find the distribution of Y .

Answer: Y denotes the minimum of $X_{i}$s.
In order to count the distribution of m(j) = P(X = j) we need to find two things.

We need to find two things.
1. Count the number of ways that we can assign $X_{1}$,$X_{2}$,...,$X_{n}$ to values between j and k at least one $X_{i}$  being assigned to j
Number of ways of getting  = 1 is $k^{n} - (k-1)^{n}$, since $k^{n}$ represents the total number of options and $(k-1)^n$ represents all of the options where non of the $X_{i}$'s are equal to 1.
For Y = 2, $k^{n} - (k-1)^{n} -[k^n-(k-1)^n]$

Generalizing for Y = j,
$(k- j + 1)^n - (k-j)^n$ ways to assign $X_{1}$,$X_{2}$,...,$X_{n}$ so that the minimum value is j.
2. Total number of possible ways to assign $X_{1}$,$X_{2}$,...,$X_{n}$ to values between 1 and k.


$X_{i}$ has k possibilities: 1,2,..,k. Total possible number of assignment is $k^{n}$.

Divide 1 by 2 to we find the distribution

$\frac{(k-j+1)^n-(k-j)^n-(k-j)^n}{k^n}$



2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors).
This machine has a manufacturer’s expected lifetime of 10 years. This means
that we expect one failure every ten years. (Include the probability statements
and R Code for each part.).

a. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a geometric. (Hint: the probability is
equivalent to not failing during the first 8 years..)

Answer: 
```{r}
p = 1/10
q = 1-p
n <- 8
pgeom(8,p,lower.tail = F)
```
The probability that the machine will fail after 8 years is 0.3874205.

```{r}
1/p
sqrt(q/p^2)
```
Expected value 10 and standard deviation 9.486833

b. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as an exponential.

Answer: 
```{r}
lambda <- 1/10
k = 8
exp(-lambda*k)
```
The probability following an exponential distribution is 0.449329.

```{r}
1/lambda
sqrt(1/lambda^2)
```
The mean and standard deviation is 10.

c. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8
years)

Answer: 
```{r}
n <- 8
p <- 1/10
q <- 1-p
k <- 0

dbinom(k, n, p)
```

The probability following a binomial distribution is  0.4304672.
```{r}
n*p
sqrt(n*p*q)
```
Following binomial distribution mean is  0.8 and standard deviation is 0.8485281.

d. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a Poisson.

Answer: 
```{r}
lambda <- 8/10
ppois(0, lambda = 0.8)
```

The probability following a poison distribution is  0.449329.
```{r}
sqrt(0.8)
```
Following Poisson distribution mean is  0.8 and standard deviation is 0.8944272.

